### 2020-04-23 README.Rmd
updated token
removed token
hexstiker readme
fixed readme typo
vignette link test

# covid19census

@@

@@

## Installation

@@

devtools::install_github("c1au6i0/covid19census", auth_token = "355580fb57d57b58228b4617c14c3f8234741715")
```

## Usage

@@

Details on the other functions and the datasets can be found in the Vignette of the package.

## U.S. Datasets and Sources

@@

## Italy: Datasets and Sources

@@

## Raw Data and other Scripts

>>>>

# covid19census  <img src='inst/img/hexsticker.png' align="right" height="139" />

@@

### Overview

@@

### Installation

@@

devtools::install_github("c1au6i0/covid19census")
```

### Usage

@@

Details on the other functions and the datasets can be found in the [vignette](vignette_how_to.html) of the package.

### U.S. Datasets and Sources

@@

### Italy: Datasets and Sources

@@

### Raw Data and other Scripts
